What public transit API logs tell us about travel flows

### 2016-01-15 paper.tex
Feedback PH processed

On highly expressive servers, such as \sparql-endpoints, query logs can play an important role in fine-tuning the underlying datastores~\cite{arias2011empirical}.
E.g., they determined that in 2011 in the context of the graph query language \sparql, most of the queries are simple and include few triple patterns and joins.
Furthermore, the graph patterns are usually star-shaped and despite triple pattern chains exist, they are generally short.
Other, more cacheable interfaces more to the left on the Linked~Data~Fragments axis~\cite{ldf}, also benefit from query logs in order to e.g., know who is using what clients to query the Web, yet the user intention is lost~\cite{usewod2015}.
This was called ``a blessing for privacy'', yet adding the user query as an HTTP header was suggested.

>>>>

On highly expressive servers, such as \sparql-endpoints, query logs can play an important role in fine-tuning the underlying datastores~\cite{arias2011empirical}.
E.g., they determined that in 2011 in the context of the graph query language \sparql, most of the queries are simple and include few triple patterns and joins.
Furthermore, the graph patterns are usually star-shaped and despite triple pattern chains exist, they are generally short.
Other, more cacheable interfaces, as introduced by Linked~Data~Fragments~\cite{ldf}, also benefit from query logs in order to e.g., know who is using what clients to query the Web, yet the user intention is lost~\cite{usewod2015}.
This was called ``a blessing for privacy'', yet adding the user query as an HTTP header was suggested.
